Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-20 paper.tex
Quadratic->Surface Tiles

~\cite{Marios:2011} & Optical (Caustics) & Quadratic Surface Tiles & Simulated Annealing \\

@@

~\cite{Papas:2012} & Optical & Quadratic Surface Tiles & Simulated Annealing \\

>>>>

~\cite{Marios:2011} & Optical (Caustics) & Piecewise Constant Tiles & Simulated Annealing \\

@@

~\cite{Papas:2012} & Optical & Piecewise Constant Tiles & Simulated Annealing \\
